---
output: github_document
bibliography: vignettes/references.bib
link-citations: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  warning = FALSE,
  message = FALSE,
  tidy = FALSE,
  fig.align = 'center',
  comment = "##",
  fig.path = "man/figures/README-"
)
```
# warmthcompetence: Warmth and Competence Detectors

Warmth and competence are the two main dimensions of social perception and judgment [@cuddy2008] . When individuals introduce or describe themselves, their audiences automatically make judgments about their warmth and competence. In the *warmthcompetence* package, we provide tools that estimate warmth and competence social perceptions from natural self-presentational language. We use pre-trained enet regression models to provide numerical representations of warmth and competence perceptions.

## Citing warmthcompetence

To generate a citation for *warmthcompetence*, please run

```{r, eval = FALSE}
citation("warmthcompetence")
```

## Installation

To install *warmthcompetence* from CRAN, use the following code in your R session:

```{r, eval = FALSE}
install.packages("warmthcompetence")
```

To install the development version from GitHub, use the following code:

```{r, eval=F}
devtools::install_github("bushraguenoun/warmthcompetence")
```

Note that some features depend on *spacyr* which must be installed separately through Python. To install *spacyr*, follow the instructions [here](https://www.rdocumentation.org/packages/spacyr/).

## Usage

*warmthcompetence* contains two main functions: `warmth()` and `competence()`. These functions can be used as described below:

```{r eval=FALSE}
competence_scores <- competence(text_vector, ID_vector, metrics = "scores")

warmth_scores <- warmth(text_vector, ID_vector, metrics = "scores")
```

In the code above, `text_vector` is the vector of texts that will be assessed for warmth or competence. `ID_vector` is a vector of IDs that will be used to identify the warmth or competence scores. The `metrics` argument allows users to decide what metrics to return. Users can return the warmth or competence scores (`metrics = "scores"`), the features that underlie the warmth or competence scores (`metrics = "features"`), or both the warmth or competence scores and the features (`metrics = "all"`). The default choice is to return the warmth or competence scores.

See `vignette("warmthcompetence")` for more details.

## Getting Help

If you have any questions or encounter any problems with the package, please submit an issue through [Github](https://github.com/bushraguenoun/warmthcompetence/issues).

You can also contact me directly at bushraguenoun\@gmail.com.

## References
